---
title: "TESFAM analysis"
author: "Laura de la Fuente and Joe Brew"
date: "June 9, 2016"
output:
  html_document:
    toc: true
    toc_float: true
    theme: yeti
---

```{r setup, include=FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = FALSE, 
               cache = FALSE)
```




```{r}
library(foreign)
library(readstata13)
library(dplyr)
library(readr)
library(sp)
library(raster)
library(leaflet)
library(ggplot2)
library(rgeos)
library(maptools)
library(plotly)
library(ggthemes)

# # Manually enter in the location of health posts
# unidades_sanitarias <- 
#   data.frame(name = c('Xinavane',
#                       '3 de fevereiro',
#                       'Iha Josina',
#                       'Mirrona',
#                       'Taninga',
#                       'Manxiane',
#                       'Palmeiras',
#                       'Chibucutsu'),
#              lat = c("25'2'815",
#                      "25'9'43",
#                      "25'5'617",
#                      "25'13'48",
#                      "25'10'74",
#                      "25'18'55",
#                      "25'15'73",
#                      "25'17'21"),
#              lng = c("32'48'308",
#                      "32'48'033",
#                      "32'55'035",
#                      "32'39'86",
#                      "32'51'12",
#                      "32'49'97",
#                      "32'51'87",
#                      "32'44'41"),
#              stringsAsFactors = FALSE)

# Read in spreadsheet (manually made by me, based on emails
# from Charfudin / Aura) of unidades_sanitarias
unidades_sanitarias <- read_csv('coordenadas_unidades_sanitarias.csv')
unidades_sanitarias <- data.frame(unidades_sanitarias)

# Define function for converting UTM to lat lon
# (not currently vectorized, need to run loop)
# convert_ll<-function(x){
#   z <- as.numeric(gsub('\"', '', unlist(strsplit(x, '<b0>|\''))))
#   as.numeric(z[1] + (z[2]/60) + (z[3]/3600))
# } 
convert_ll <- function(x){
  z <- unlist(strsplit(x, '°|\'|"'))
  as.numeric(z[1]) + (as.numeric(z[2])/60) + (as.numeric(z[3])/3600)
}

# Convert the coordinates of health posts to lat long
unidades_sanitarias$lon <-
  unidades_sanitarias$x <-
  unidades_sanitarias$y <- NA
for (i in 1:nrow(unidades_sanitarias)){
  unidades_sanitarias$x[i] <-
  unidades_sanitarias$lon[i] <-
  unidades_sanitarias$lng[i] <- 
  as.numeric(convert_ll(unidades_sanitarias$lng[i]))
  unidades_sanitarias$y[i] <-
  unidades_sanitarias$lat[i] <-
  as.numeric(convert_ll(unidades_sanitarias$lat[i]) * -1)
}

# Make it all numeric
for (j in 2:ncol(unidades_sanitarias)){
  unidades_sanitarias[,j] <-
    as.numeric(unidades_sanitarias[,j])
}

# Make spatial
coordinates(unidades_sanitarias) <- ~x+y
proj4string(unidades_sanitarias) <- 
  CRS("+proj=longlat +ellps=WGS84 +datum=WGS84")

# Read in tesfam
tesfam <- read.dta13('TESFAM_variables_selecion_02.dta')

# Read in coords
coords <- read_csv('Coordenadas.csv')
coords <- coords[!duplicated(coords$Family_id),]

# Join tesfam and coords
tesfam <- left_join(x = tesfam,
                    y = coords,
                    by = c('familynum' = 'Family_id')) %>%
  # filter(!duplicated(familynum)) %>%
  mutate(lon = LongUTM,
         lat = LatUTM,
         x = LongUTM,
         y = LatUTM)

# Make tesfam spatial
tesfam <- tesfam[!is.na(tesfam$x),]
coordinates(tesfam) <- ~x+y

# Make tesfam latlong
proj4string(tesfam) <- CRS("+proj=utm +zone=36 +south")
tesfam <- spTransform(tesfam,CRS("+proj=longlat +ellps=WGS84 +datum=WGS84"))

# Overwrite lat long
tesfam$lon <- coordinates(tesfam)[,1]
tesfam$lat <- coordinates(tesfam)[,2]

# Get distance to and name of nearest health center for each
# person in tesfam
tesfam$health_post <- NA
tesfam$distance <- NA

# Now calculate distance
distances <- 
  spDists(x = tesfam, 
        y = unidades_sanitarias,
        longlat = TRUE,
        diagonal = FALSE)

# Add distances to coordenadas dataframe
tesfam$distance <- 
  apply(distances, 1, function(x){x[which.min(x)]})

# Get nearest center
tesfam$health_post <- 
  apply(distances,
        1, function(x){unidades_sanitarias$name[which.min(x)]})


# Get mozambique shapefile
moz <- getData('GADM', country = 'MOZ', level = 2)
moz3 <- getData('GADM', country = 'MOZ', level = 3)

# Subset to manhica
man <- moz[moz@data$NAME_2 == 'Manhiça',]
man3 <- moz3[moz3@data$NAME_2 == 'Manhiça',]

# Fortify
moz3_fortified <- fortify(moz3, region = 'NAME_3')
man3_fortified <- fortify(man3, region = 'NAME_3')


# Create a color based on testgroup
tesfam$color <-
  ifelse(tesfam$testgroup == 'HBT', 'blue',
         ifelse(tesfam$testgroup == 'VCT', 'darkorange',
                ifelse(tesfam$testgroup == "PICT", 'darkgreen',
                       NA)))

# Create a shape based on attrition
tesfam$shape <- 
  ifelse(tesfam$abandono_3mo == 1, 17,
         ifelse(tesfam$abandono_3mo == 0, 16, NA))
```

# Static maps

## Basic static map

```{r}
# Plot using base map
plot(man3, col = 'grey', border = 'white')
# People points
points(tesfam, 
       col = adjustcolor(tesfam$color, alpha.f = 0.7), 
       pch = tesfam$shape, 
       cex = 0.2)
# Health center points
points(unidades_sanitarias,
       col = adjustcolor('darkred', alpha.f = 0.7),
       pch = 1)
# Add legend
legend('topleft',
       col = c('blue', 'darkorange', 'darkgreen'),
       legend = c('HBT', 'VCT', 'PICT'),
       title = 'Testing venue',
       pch = 1)
legend('bottomright',
       pch = c(17, 16),
       legend = c('Lost to follow-up', 'Followed-up'),
       title = 'Linkage at 3 months')
legend('topright',
       pch = 1,
       col = adjustcolor('darkred', alpha.f = 0.8),
       legend = 'Health centers')
title(main = 'HIV cascade for TESFAM cohort at 3 months')


```

## Fancy static maps

```{r}

cols <- c('blue', 'darkorange', 'darkgreen')
g <- 
  ggplot() +
coord_map() +
  geom_polygon(data = man3_fortified,
               aes(x = long, y =lat, group = group), 
               fill = 'grey', color = 'white') +
  geom_point(data = tesfam@data %>% 
               mutate(`Follow up` = ifelse(abandono_3mo == 1, 'Lost',
                                                                'Not lost')),
              aes(x = lon, y = lat,
                  color = testgroup,
                  pch = `Follow up`),
             size = 0.5) +
  scale_color_manual(name = 'Testing venue',
                     values = cols) +
  theme_fivethirtyeight() +
  xlab('Longitude') +
  ylab('Latitude') +
  labs(title = 'Spatial distribution',
       subtitle = '3 months follow-up')
g
```

```{r}
# Same as above but at 6 months

cols <- c('blue', 'darkorange', 'darkgreen')
g <- 
  ggplot() +
coord_map() +
  geom_polygon(data = man3_fortified,
               aes(x = long, y =lat, group = group), 
               fill = 'grey', color = 'white') +
  geom_point(data = tesfam@data %>% 
               mutate(`Follow up` = ifelse(abandono_6mo == 1, 'Lost',
                                                                'Not lost')),
              aes(x = lon, y = lat,
                  color = testgroup,
                  pch = `Follow up`),
             size = 0.5) +
  scale_color_manual(name = 'Testing venue',
                     values = cols) +
  theme_fivethirtyeight() +
  xlab('Longitude') +
  ylab('Latitude') +
  labs(title = 'Spatial distribution',
       subtitle = '6 months follow-up')
g
```

```{r}
# Distance to health post
g <- 
  ggplot() +
coord_map() +
  geom_polygon(data = man3_fortified,
               aes(x = long, y =lat, group = group), 
               fill = 'grey', color = 'white') +
  geom_point(data = tesfam@data %>% 
               mutate(`Follow up` = ifelse(abandono_6mo == 1, 'Lost',
                                                                'Not lost'),
                      `Distance to health post` = distance),
              aes(x = lon, y = lat,
                  color = `Distance to health post`,
                  pch = `Follow up`),
             size = 0.5) +
    geom_point(data = unidades_sanitarias@data,
               aes(x = lon, y = lat),
             color = 'red') +
  # scale_color_gradientn(colours = terrain.colors(10)) +
  theme_fivethirtyeight(base_size = 12) +
  xlab('Longitude') +
  ylab('Latitude') +
  labs(title = 'Distance to nearest\nhealth post',
       subtitle = '(The red dots are the health facilities)')
g
```

# Interactive maps

Patients who are lost to follow up are represented by smaller, semi-transparent points.

## Basic interactive map

Create a box on the map to zoom in. Double-click to zoom out. Click on the legend to remove or add points. Mouse over the points to get more details.

```{r}
ggplotly(g)
```

## Fancy interactive satellite map

The blue markers are health posts.

```{r}
library(leaflet)
library(RColorBrewer)

colspal <- brewer.pal(3, 'Spectral')
cols <- colspal[as.numeric(factor(tesfam$testgroup))]

# Subset data to only include those that got lost
lost <- data.frame(tesfam) %>% filter(abandono_3mo == 1)
not_lost <- data.frame(tesfam) %>% filter(abandono_3mo == 0)

# Get colors
lost_cols <- colspal[as.numeric(factor(lost$testgroup))]
not_lost_cols <- colspal[as.numeric(factor(not_lost$testgroup))]


leaflet() %>%
  # addProviderTiles('Stamen.Watercolor') %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addCircleMarkers(lng = lost$lon,
                  lat = lost$lat,
                  color = lost_cols,
                  fillColor = lost_cols,
                  radius = 2.5,
                  opacity = 0,
                  fillOpacity = 0.5,
                  popup = paste0('Study number: ', lost$ssid, '\n',
                                 'Group: ', lost$testgroup, '\n',
                                 '3 month followup: ',
                                 ifelse(lost$abandono_3mo == 1, 'Lost',
                                        'Not lost'))) %>%
      addLegend("bottomright", colors= colspal,
                labels=c('HBT', 'VCT', 'PICT'), title="Study arm") %>%
    addCircleMarkers(lng = not_lost$lon,
                  lat = not_lost$lat,
                  color = not_lost_cols,
                  fillColor = not_lost_cols,
                  radius = 5,
                  opacity = 0,
                  fillOpacity = 1,
                  popup = paste0('Study number: ', not_lost$ssid, '\n',
                                 'Group: ', not_lost$testgroup, '\n',
                                 '3 month followup: ', 
                                 ifelse(not_lost$abandono_3mo == 1, 'Lost',
                                        'Not not_lost'))) %>% #,
                  # clusterOptions = markerClusterOptions()) 
  addMarkers(lng = unidades_sanitarias@data$lng,
             lat = unidades_sanitarias@data$lat,
             popup = unidades_sanitarias@data$name)
```


## Fancy interactive road map

The blue markers are health posts.

```{r}
library(leaflet)
library(RColorBrewer)
colspal <- brewer.pal(3, 'Spectral')
cols <- colspal[as.numeric(factor(tesfam$testgroup))]

# Subset data to only include those that got lost
lost <- data.frame(tesfam) %>% filter(abandono_3mo == 1)
not_lost <- data.frame(tesfam) %>% filter(abandono_3mo == 0)

# Get colors
lost_cols <- colspal[as.numeric(factor(lost$testgroup))]
not_lost_cols <- colspal[as.numeric(factor(not_lost$testgroup))]


leaflet() %>%
  # addProviderTiles('Stamen.Watercolor') %>%
  # addProviderTiles("Esri.WorldImagery") %>%
  addProviderTiles('OpenStreetMap.BlackAndWhite') %>%
  addCircleMarkers(lng = lost$lon,
                  lat = lost$lat,
                  color = lost_cols,
                  fillColor = lost_cols,
                  radius = 2.5,
                  opacity = 0,
                  fillOpacity = 0.5,
                  popup = paste0('Study number: ', lost$ssid, '\n',
                                 'Group: ', lost$testgroup, '\n',
                                 '3 month followup: ',
                                 ifelse(lost$abandono_3mo == 1, 'Lost',
                                        'Not lost'))) %>%
      addLegend("bottomright", colors= colspal,
                labels=c('HBT', 'VCT', 'PICT'), title="Study arm") %>%
    addCircleMarkers(lng = not_lost$lon,
                  lat = not_lost$lat,
                  color = not_lost_cols,
                  fillColor = not_lost_cols,
                  radius = 5,
                  opacity = 0,
                  fillOpacity = 1,
                  popup = paste0('Study number: ', not_lost$ssid, '\n',
                                 'Group: ', not_lost$testgroup, '\n',
                                 '3 month followup: ', 
                                 ifelse(not_lost$abandono_3mo == 1, 'Lost',
                                        'Not not_lost'))) %>%#,
                  # clusterOptions = markerClusterOptions()) 
    addMarkers(lng = unidades_sanitarias@data$lng,
             lat = unidades_sanitarias@data$lat,
             popup = unidades_sanitarias@data$name)

```

# Analysis

Association between distance to center and likelihood of being lost to follow-up. 

```{r}
# Logistic regression model
fit <- glm(abandono_6mo ~ distance, 
           data = tesfam@data,
           family = binomial('logit'))
ors <- exp(cbind(OR = coef(fit), confint(fit))) %>%
  data.frame
```

Using a simple logistic regression model, we estimate that for every 1 kilometer further from a health post, the odds of being lost to follow-up at 6 months increases by `r round((ors$OR[2] - 1) * 100, digits = 2)`% (OR of `r ors$OR[2]`, 95% confidence interval of `r ors$X2.5..[2]` to `r ors$X97.5..[2]`). Our fitted model can be visualized like this.

```{r}
fake <- data.frame(distance = seq(0, 25, length = 100))
predictions <- predict(fit, fake, type = 'link', se = TRUE)
fake$predicted <- plogis(predictions$fit)
fake$lwr <- plogis(predictions$fit - (1.96 * predictions$se.fit))
fake$upr <- plogis(predictions$fit + (1.96 * predictions$se.fit))

# Gather
fake_gathered <- tidyr::gather(data = fake,
                               key, 
                               value, 
                               predicted:upr)

ggplot(data = fake) +
  geom_linerange(aes(x = distance,
                     ymax = upr,
                     ymin = lwr),
                 alpha = 0.6) +
  geom_line(aes(x = distance, y = predicted),
            color = 'red') +
  labs(title = 'Distance matters',
       subtitle = 'Association of distance to health post and getting lost') +
  theme_economist() +
    xlab('Kilometers to health post') +
  ylab('Likelihood of being lost to follow-up at 6 mo') 
```


