---
title: "TESFAM Maps"
author: "Laura de la Fuente and Joe Brew"
date: "June 9, 2016"
output:
  html_document:
    toc: true
    toc_float: true
    theme: yeti
---

```{r setup, include=FALSE}
# Basic knitr options
library(knitr)
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = FALSE, 
               cache = FALSE)
```




```{r}
library(foreign)
library(readstata13)
library(dplyr)
library(readr)
library(sp)
library(raster)
library(leaflet)
library(ggplot2)
library(rgeos)
library(maptools)
library(plotly)
library(ggthemes)

# Read in tesfam
tesfam <- read.dta13('TESFAM_variables_selecion_02.dta')

# Read in coords
coords <- read_csv('Coordenadas.csv')
coords <- coords[!duplicated(coords$Family_id),]

# Join tesfam and coords
tesfam <- left_join(x = tesfam,
                    y = coords,
                    by = c('familynum' = 'Family_id')) %>%
  # filter(!duplicated(familynum)) %>%
  mutate(lon = LongUTM,
         lat = LatUTM,
         x = LongUTM,
         y = LatUTM)

# Make tesfam spatial
tesfam <- tesfam[!is.na(tesfam$x),]
coordinates(tesfam) <- ~x+y

# Make tesfam latlong
proj4string(tesfam) <- CRS("+proj=utm +zone=36 +south")
tesfam <- spTransform(tesfam,CRS("+proj=longlat +ellps=WGS84 +datum=WGS84"))

# Overwrite lat long
tesfam$lon <- coordinates(tesfam)[,1]
tesfam$lat <- coordinates(tesfam)[,2]

# Get mozambique shapefile
moz <- getData('GADM', country = 'MOZ', level = 2)
moz3 <- getData('GADM', country = 'MOZ', level = 3)

# Subset to manhica
man <- moz[moz@data$NAME_2 == 'Manhiça',]
man3 <- moz3[moz3@data$NAME_2 == 'Manhiça',]

# Fortify
moz3_fortified <- fortify(moz3, region = 'NAME_3')
man3_fortified <- fortify(man3, region = 'NAME_3')


# Create a color based on testgroup
tesfam$color <-
  ifelse(tesfam$testgroup == 'HBT', 'blue',
         ifelse(tesfam$testgroup == 'VCT', 'darkorange',
                ifelse(tesfam$testgroup == "PICT", 'darkgreen',
                       NA)))

# Create a shape based on attrition
tesfam$shape <- 
  ifelse(tesfam$abandono_3mo == 1, 17,
         ifelse(tesfam$abandono_3mo == 0, 16, NA))
```

# Static maps

## Basic static map

```{r}
# Plot using base map
plot(man3, col = 'grey', border = 'white')
points(tesfam, 
       col = adjustcolor(tesfam$color, alpha.f = 0.7), 
       pch = tesfam$shape, 
       cex = 0.2)

# Add legend
legend('topleft',
       col = c('blue', 'darkorange', 'darkgreen'),
       legend = c('HBT', 'VCT', 'PICT'),
       title = 'Testing venue',
       pch = 1)
legend('bottomright',
       pch = c(17, 16),
       legend = c('Lost to follow-up', 'Followed-up'),
       title = 'Linkage at 3 months')
title(main = 'HIV cascade for TESFAM cohort at 3 months')

```

## Fancy static map

```{r}

cols <- c('blue', 'darkorange', 'darkgreen')
g <- 
  ggplot() +
coord_map() +
  geom_polygon(data = man3_fortified,
               aes(x = long, y =lat, group = group), 
               fill = 'grey', color = 'white') +
  geom_point(data = tesfam@data %>% 
               mutate(`Follow up` = ifelse(abandono_3mo == 1, 'Lost',
                                                                'Not lost')),
              aes(x = lon, y = lat,
                  color = testgroup,
                  pch = `Follow up`)) +
  scale_color_manual(name = 'Testing venue',
                     values = cols) +
  theme_fivethirtyeight() +
  xlab('Longitude') +
  ylab('Latitude') +
  labs(title = 'Spatial distribution',
       subtitle = '3 months')
g
```

# Interactive maps

Patients who are lost to follow up are represented by smaller, semi-transparent points.

## Basic interactive map

Create a box on the map to zoom in. Double-click to zoom out. Click on the legend to remove or add points. Mouse over the points to get more details.

```{r}
ggplotly(g)
```

## Fancy interactive satellite map

```{r}
library(leaflet)
library(RColorBrewer)

colspal <- brewer.pal(3, 'Spectral')
cols <- colspal[as.numeric(factor(tesfam$testgroup))]

# Subset data to only include those that got lost
lost <- data.frame(tesfam) %>% filter(abandono_3mo == 1)
not_lost <- data.frame(tesfam) %>% filter(abandono_3mo == 0)

# Get colors
lost_cols <- colspal[as.numeric(factor(lost$testgroup))]
not_lost_cols <- colspal[as.numeric(factor(not_lost$testgroup))]


leaflet() %>%
  # addProviderTiles('Stamen.Watercolor') %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addCircleMarkers(lng = lost$lon,
                  lat = lost$lat,
                  color = lost_cols,
                  fillColor = lost_cols,
                  radius = 2.5,
                  opacity = 0,
                  fillOpacity = 0.5,
                  popup = paste0('Study number: ', lost$ssid, '\n',
                                 'Group: ', lost$testgroup, '\n',
                                 '3 month followup: ',
                                 ifelse(lost$abandono_3mo == 1, 'Lost',
                                        'Not lost'))) %>%
      addLegend("bottomright", colors= colspal,
                labels=c('HBT', 'VCT', 'PICT'), title="Study arm") %>%
    addCircleMarkers(lng = not_lost$lon,
                  lat = not_lost$lat,
                  color = not_lost_cols,
                  fillColor = not_lost_cols,
                  radius = 5,
                  opacity = 0,
                  fillOpacity = 1,
                  popup = paste0('Study number: ', not_lost$ssid, '\n',
                                 'Group: ', not_lost$testgroup, '\n',
                                 '3 month followup: ', 
                                 ifelse(not_lost$abandono_3mo == 1, 'Lost',
                                        'Not not_lost')))#,
                  # clusterOptions = markerClusterOptions()) 
```


## Fancy interactive road map

```{r}
library(leaflet)
library(RColorBrewer)
colspal <- brewer.pal(3, 'Spectral')
cols <- colspal[as.numeric(factor(tesfam$testgroup))]

# Subset data to only include those that got lost
lost <- data.frame(tesfam) %>% filter(abandono_3mo == 1)
not_lost <- data.frame(tesfam) %>% filter(abandono_3mo == 0)

# Get colors
lost_cols <- colspal[as.numeric(factor(lost$testgroup))]
not_lost_cols <- colspal[as.numeric(factor(not_lost$testgroup))]


leaflet() %>%
  # addProviderTiles('Stamen.Watercolor') %>%
  # addProviderTiles("Esri.WorldImagery") %>%
  addProviderTiles('OpenStreetMap.BlackAndWhite') %>%
  addCircleMarkers(lng = lost$lon,
                  lat = lost$lat,
                  color = lost_cols,
                  fillColor = lost_cols,
                  radius = 2.5,
                  opacity = 0,
                  fillOpacity = 0.5,
                  popup = paste0('Study number: ', lost$ssid, '\n',
                                 'Group: ', lost$testgroup, '\n',
                                 '3 month followup: ',
                                 ifelse(lost$abandono_3mo == 1, 'Lost',
                                        'Not lost'))) %>%
      addLegend("bottomright", colors= colspal,
                labels=c('HBT', 'VCT', 'PICT'), title="Study arm") %>%
    addCircleMarkers(lng = not_lost$lon,
                  lat = not_lost$lat,
                  color = not_lost_cols,
                  fillColor = not_lost_cols,
                  radius = 5,
                  opacity = 0,
                  fillOpacity = 1,
                  popup = paste0('Study number: ', not_lost$ssid, '\n',
                                 'Group: ', not_lost$testgroup, '\n',
                                 '3 month followup: ', 
                                 ifelse(not_lost$abandono_3mo == 1, 'Lost',
                                        'Not not_lost')))#,
                  # clusterOptions = markerClusterOptions()) 
  

```
